---
title: "Untitled"
author: "Richard J. Telford"
date: "8/27/2020"
output: pdf_document
classoption: a4paper
bibliography: Rmd/TDT2.bib
csl: Rmd/elsevier-harvard_rjt.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("drake")
loadd(moments_by_climate)
```

## Methods

### Software

All analyses were done in R v. `r getRversion()` [@R] and used
traitstrap v. `r packageVersion("traitstrap")` [@traitstrap] to impute traits,
e1071 v. `r packageVersion("e1071")` [@e1071] to calculate moments,
and tidyverse v. `r packageVersion("tidyverse")` [@tidyverse].
Packages drake v. `r packageVersion("drake")` [@drake], 
rmarkdown `r packageVersion("rmarkdown")` [@rmarkdown1] and
renv v. `r packageVersion("renv")` [@renv] were used to ensure reproducibility.
Code to reproduce all the analyses is archived at [https://github.com/richardjtelford/trait-driver-analysis](https://github.com/richardjtelford/trait-driver-analysis).

## Results

### Figure 2
```{r trait-climate, eval = TRUE, echo = FALSE}
readd(moments_by_climate)
```

### Figure 4
```{r conv-div, eval = TRUE, echo = FALSE, fig.height = 15}
readd(conv_div_plot)
```

### Figure 5
```{r eucledian, eval = TRUE, echo = FALSE}
readd(euclidean_distance)
```

### Figure 6
```{r var-ske-kurt, eval = TRUE, echo = FALSE, fig.height = 10}
readd(variance_plot)
readd(skewness_plot)
readd(kurtosis_plot)
```


## References
